### 2021-06-10 paper/report.tex
Moved on with final paragraphs.

Alternative:
\begin{itemize}
    \item Germany quite lenient on home office relative to other countries (employer had
          to allow)
    \item Testing: Rapid tests are cheap (less than 1\euro), just a nuisance.
\end{itemize}

Results
\begin{itemize}
    \item Advantage of testing in both cases: Recurrent. Small cost relative to other
          stuff. Certain publicness.
    \item Mandatory tests: Screening effect for hard-to-reach populations (do not
          consider in this paper, also due to poor data in DE)
\end{itemize}

>>>>

Figure~\ref{fig:workplace_scenarios} shows that with a large fraction of employees receiving tests, testing at the workplace has larger effects than changing requirements to work from home. Whether the share of workers working at the usual workplace is reduced or increased by ten percent hardly has an effect on infection rates. Making testing mandatory twice a week---assuming independet compliance by employers and workers or 95\% each---would have reduced infections by 13\%. Reducing rapid tests offers by employers to the level of March would have increased them by the same amount.

Despite these large effects, the results on testing likely understate the benefits. Disadvantaged groups of the population are less likely to be reached by testing campaigns; at the same time they have a higher risk to contract CoViD-19. Mandatory tests at school and at the workplace would help reach these groups, too. The same goes for ...

The tests are

 Testing: Rapid tests are cheap (less than 1\euro), just a nuisance.

Results
\begin{itemize}
    \item Advantage of testing in both cases: Recurrent. Small cost relative to other
          stuff. Certain publicness.
\end{itemize}
